Correspondence Analysis of Two Mode Networks

### 2025-01-29 main-R1.tex
Updates from Overleaf

\citet{borgatti1997network} provided an early in-depth considerations of CA in the context of two-mode network data analysis with an emphasis on the visualization aspect. The discussion was placed in a section on ``visual representations of 2-mode data,'' and naturally focused almost exclusively on the uses of CA as visualization technique. According to \citet[246]{borgatti1997network}, CA ``can be seen as a method for representing points in a metric space such that distances between the points are meaningful.'' More specifically, \citet{borgatti1997network}, also using the Southern Women data as illustration,  claimed that in the CA map, points representing the women will appear closer if the women attend ``mostly the same events,'' and conversely points representing the events will be placed near one another if the events were attended by ``mostly the same women,'' and that women and events would appear closer in the plot if ``those women attended those events.'' \citet[247-249]{borgatti1997network} then went on to focus on various limitations of CA as visualization tool, noting that given the limiting range of dichotomous network data, two-dimensional representations ``will almost always be severely inaccurate or misleading.'' They also noted that since CA is a technique designed to deal with valued frequency data, its use with binary network data would lead to dimensional scores that would be either ``meaningless'' or ``difficult to interpret.'' Finally, they noted that since distances in the CA biplot are not Euclidean they would mislead interpreters who would try to impose such a metric to make sense of them.

@@

@@

Both $\mathbf{P}_{pp}$ and $\mathbf{P}_{gg}$ are square ($P \times |P|$ and $|G| \times |G|$) respectively) degree-normalized projection matrices linking people and groups. For the Southern Women data, they are show in Figure~\ref{fig:p-norm} and~\ref{fig:g-norm}.

>>>>

\citet{borgatti1997network} provided an early in-depth consideration of CA in the context of two-mode network data analysis with an emphasis on the visualization aspect. The discussion was placed in a section on ``visual representations of 2-mode data,'' and naturally focused almost exclusively on the uses of CA as a visualization technique. According to \citet[246]{borgatti1997network}, CA ``can be seen as a method for representing points in a metric space such that distances between the points are meaningful.'' More specifically, \citet{borgatti1997network}, also using the Southern Women data as illustration,  claimed that in the CA map, points representing the women will appear closer if the women attend ``mostly the same events.'' Conversely, points representing the events will be placed near one another if the events were attended by ``mostly the same women,'' and that women and events would appear closer in the plot if ``those women attended those events.'' \citet[247-249]{borgatti1997network} then went on to focus on various limitations of CA as a visualization tool, noting that given the limiting range of dichotomous network data, two-dimensional representations ``will almost always be severely inaccurate or misleading.'' They also noted that since CA is a technique designed to deal with valued frequency data, its use with binary network data would lead to dimensional scores that would be either ``meaningless'' or ``difficult to interpret.'' Finally, they noted that since distances in the CA biplot are not Euclidean they would mislead interpreters who would try to impose such a metric to make sense of them.

@@

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-norm.png}
            \caption{Degree-weighted projection (People).}
            \label{fig:ca-reord}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-norm.png}
            \caption{Degree-weighted projection (Groups).}
            \label{fig:bon-reord}
    \end{subfigure}
    \caption{}
    \label{fig:dwproj}
\end{figure}

@@

Both $\mathbf{P}_{pp}$ and $\mathbf{P}_{gg}$ are square ($P \times |P|$ and $|G| \times |G|$) respectively) degree-normalized projection matrices linking people and groups. For the Southern Women data, they are shown in Figure~\ref{fig:dwproj}.
